class: inverse, center, middle
# Conclusion

---
class: center
# {gtsummary}
.large[
• Every function is documented further in the help file •

• Check out the package website for vignettes including detailed examples and explanations •

<img src = "images/open-book-white.png" width="2.4%" height="2.4%"> {gtsummary} documentation <a href="http://www.danieldsjoberg.com/gtsummary/">danieldsjoberg.com/gtsummary/</a>

<img src = "images/github_icon.png" width="2.4%" height="2.4%"> {gtsummary} package <a href="https://github.com/ddsjoberg/gtsummary">github.com/ddsjoberg/gtsummary</a>

<img src = "images/slide_show_icon.png" width="2.4%" height="2.4%"> slides at <a href="http://www.danieldsjoberg.com/gt-and-gtsummary-presentation">danieldsjoberg.com/gt-and-gtsummary-presentation</a>  

<img src = "images/github_icon.png" width="2.4%" height="2.4%"> source code for slides at <a href="https://github.com/ddsjoberg/gt-and-gtsummary-presentation">github.com/ddsjoberg/gt-and-gtsummary-presentation</a>

<img src = "images/github_icon.png" width="2.4%" height="2.4%"> {gt} package <a href="https://github.com/rstudio/gt">github.com/rstudio/gt</a>
]

???

Go star {gtsummary} on GitHub...we're already to 50+!

---

# {gtsummary} Advanced

.large[
{gtsummary} output is a list that prints as a {gt} table.
]
```{r}
names(tbl_summary_1)
```

.pull-left[
```{r}
pluck(tbl_summary_1, "table_body") %>% head()
```
]
.pull-right[
```{r}
pluck(tbl_summary_1, "gt_calls") %>% head(n = 4)
```
]

???

If there is time, review the structure of a {gtsummary} object

Essentially, what is going on is that the {gt} calls on the right are called on the table on the left whenever the object is printed.

Understanding this structure will help you modify if you need.  If there is a {gt} call that formats in a way you don't like, convert your object with `as_gt()` and use the `omit =` argument to leave out the gt call you don't like.

You can replace it with whatever you choose.

---
# Download {gtsummary} today!

```{r include = FALSE, echo=FALSE}
dl <- cranlogs::cran_downloads(packages = "gtsummary", from = "2019-05-01", to = "last-day")

library(lubridate)
library(scales)

dlmonth <- dl %>% 
  group_by(month = floor_date(date, "month")) %>% 
  summarize(amount = sum(count)) %>% 
  filter(month != "2020-02-01")

p <- ggplot(dlmonth, aes(x = month, y = amount)) +
  geom_line() + 
  xlab("") +
  coord_cartesian(ylim = c(0,1100)) +
  labs(
    title = "{gtsummary} CRAN downloads",
    subtitle = "source: cranlogs"
  ) +
  ylab("Downloads/Month") +
  # scale_x_date(
  #   date_breaks = "1 month",
  #   labels = date_format("%m-%Y")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))  +
   geom_vline(xintercept = as.numeric(as.Date("2019-05-01")),
              linetype = 4,
              color = "seagreen")
  

p
```

---
# Thank you

Author/Maintainer: Daniel Sjoberg

Authors: Margie Hannum, Karissa Whiting, Emily Zabor, Michael Curry

Contributors: Esther Drill, Jessica Flynn
