class: inverse, center, middle
# Conclusion

---
class: center
# {gtsummary}
.large[
• Every function is documented further in the help file •

• Check out the package website for vignettes including detailed examples and explanations •

<img src = "images/open-book-white.png" width="2.4%" height="2.4%"> {gtsummary} documentation <a href="http://www.danieldsjoberg.com/gtsummary/">danieldsjoberg.com/gtsummary/</a>

<img src = "images/github_icon.png" width="2.4%" height="2.4%"> {gtsummary} package <a href="https://github.com/ddsjoberg/gtsummary">github.com/ddsjoberg/gtsummary</a>

<img src = "images/slide_show_icon.png" width="2.4%" height="2.4%"> slides at <a href="http://www.danieldsjoberg.com/gt-and-gtsummary-presentation">danieldsjoberg.com/gt-and-gtsummary-presentation</a>  

<img src = "images/github_icon.png" width="2.4%" height="2.4%"> source code for slides at <a href="https://github.com/ddsjoberg/gt-and-gtsummary-presentation">github.com/ddsjoberg/gt-and-gtsummary-presentation</a>

<img src = "images/github_icon.png" width="2.4%" height="2.4%"> {gt} package <a href="https://github.com/rstudio/gt">github.com/rstudio/gt</a>
]

???

Go star {gtsummary} on GitHub...we're already to 50+!

---

# {gtsummary} Advanced

.large[
{gtsummary} output is a list that prints as a {gt} table.
]
```{r}
names(tbl_summary_1)
```

.pull-left[
```{r}
pluck(tbl_summary_1, "table_body") %>% head()
```
]
.pull-right[
```{r}
pluck(tbl_summary_1, "gt_calls") %>% head(n = 4)
```
]

???

If there is time, review the structure of a {gtsummary} object

Essentially, what is going on is that the {gt} calls on the right are called on the table on the left whenever the object is printed.

Understanding this structure will help you modify if you need.  If there is a {gt} call that formats in a way you don't like, convert your object with `as_gt()` and use the `omit =` argument to leave out the gt call you don't like.

You can replace it with whatever you choose.