class: inverse, center, middle

# Conclusion

---

# {gtsummary} v1.2.6 - Package Website

.large[
* Package Website: http://www.danieldsjoberg.com/gtsummary/

  * <img src = "images/open-book-white.png" width="2.4%" height="2.4%"> Installation instructions
  
  * <img src = "images/open-book-white.png" width="2.4%" height="2.4%"> Thorough documentation on every function
  
  * <img src = "images/open-book-white.png" width="2.4%" height="2.4%"> Detailed tutorials 
  
* Install {gtsummary} from CRAN with the following code: 
]

``` {r, eval=FALSE}
install.packages("gtsummary")          
```

.large[
* Also recommended to install the development version of {gt} from GitHub.
]
``` {r, eval=FALSE}
install.packages("remotes")
remotes::install_github("rstudio/gt")        
```



???
- visit the website and give quick tour
---

class: center
# {gtsummary}
.large[
• Every function is documented further in the help file •

• Check out the package website for vignettes including detailed examples and explanations •

<img src = "images/open-book-white.png" width="2.4%" height="2.4%"> {gtsummary} documentation/website <a href="http://www.danieldsjoberg.com/gtsummary/">danieldsjoberg.com/gtsummary/</a>

<img src = "images/github_icon.png" width="2.4%" height="2.4%"> {gtsummary} package <a href="https://github.com/ddsjoberg/gtsummary">github.com/ddsjoberg/gtsummary</a>

<img src = "images/slide_show_icon.png" width="2.4%" height="2.4%"> slides at <a href="https://github.com/margarethannum/gtsummary-presentation-rladies">github.com/margarethannum/gtsummary-presentation-rladies</a>  

<img src = "images/github_icon.png" width="2.4%" height="2.4%"> source code for slides at <a href="https://github.com/margarethannum/gtsummary-presentation-rladies">github.com/margarethannum/gtsummary-presentation-rladies</a>

<img src = "images/github_icon.png" width="2.4%" height="2.4%"> {gt} package <a href="https://github.com/rstudio/gt">github.com/rstudio/gt</a>
]

???

Go star {gtsummary} on GitHub...we're already to 50+!


---
# Questions?

```{r include = FALSE, echo=FALSE, eval=FALSE}
dl <- cranlogs::cran_downloads(packages = "gtsummary", from = "2019-05-01", to = "last-day")

library(lubridate)
library(scales)

dlmonth <- dl %>% 
  group_by(month = floor_date(date, "month")) %>% 
  summarize(amount = sum(count)) %>% 
  filter(month != "2020-02-01")

p <- ggplot(dlmonth, aes(x = month, y = amount)) +
  geom_line() + 
  xlab("") +
  coord_cartesian(ylim = c(0,1100)) +
  labs(
    title = "{gtsummary} CRAN downloads",
    subtitle = "source: cranlogs"
  ) +
  ylab("Downloads/Month") +
  # scale_x_date(
  #   date_breaks = "1 month",
  #   labels = date_format("%m-%Y")) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))  #+
   # geom_vline(xintercept = as.numeric(as.Date("2019-05-01")),
   #            linetype = 4,
   #            color = "seagreen")
  

p
```

---
# Thank you

.large[
Author/Maintainer: **Daniel Sjoberg** (Many slides & materials taken from his presentation!)

Authors: Margie Hannum, Karissa Whiting, Emily Zabor, Michael Curry

Contributors: Esther Drill, Jessica Flynn
]
